Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-30 system.tex
capitalize Gist in this context

Using GitHub for storage and versioning also exposes other capabilities
that can be invoked with JSON and HTTP.
Particularly, we can provide full text search using Apache SOLR.
SOLR is scalable, can index in near-realtime, supports multiple character sets,
indexes several common types of documents, and has schemas and faceted search.
%
Integrating existing services and software components, especially open source,
instead of implementing custom code is a trend in the software industry, and
is very positive for systems research and prototyping in visual analytics.
By adopting existing technology, small teams with limited resoures can explore
novel ideas toward the improvement of large, complex software ecosystems.
In our case, even though this approach involved learning standards not directly
related to visual analytics, our early decision to use the GitHub gist API
turned out to be successful. Future projects could gain many of the same benefits
by adopting this strategy. In fact, it will be essential for technology adoption
and transfer, because it is almost impossible for any one tool or platform to
``own'' or support the entire visual analytics process.
\stephen{Are we preaching too much?}

>>>>

Using GitHub for storage and versioning also exposes other capabilities
that can be invoked with JSON and HTTP.
Particularly, we can provide full text search using Apache SOLR.
SOLR is scalable, can index in near-realtime, supports multiple character sets,
indexes several common types of documents, and has schemas and faceted search.
%
Integrating existing services and software components, especially open source,
instead of implementing custom code is a trend in the software industry, and
is very positive for systems research and prototyping in visual analytics.
By adopting existing technology, small teams with limited resoures can explore
novel ideas toward the improvement of large, complex software ecosystems.
In our case, even though this approach involved learning standards not directly
related to visual analytics, our early decision to use the GitHub Gist API
turned out to be successful. Future projects could gain many of the same benefits
by adopting this strategy. In fact, it will be essential for technology adoption
and transfer, because it is almost impossible for any one tool or platform to
``own'' or support the entire visual analytics process.
\stephen{Are we preaching too much?}
